---
title: "Process raw non-anonymous data into anonymous form"
author: "Ashley Leung, Alex Tunkel, and Dan Yurovsky"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
    number_sections: no
    theme: lumen
    toc: no
    toc_float: no
  pdf_document:
    toc: no
---
```{r, message=FALSE, warning=FALSE, show = F}
library(tidytext)
library(janitor)
library(knitr)
library(here)
library(tidyboot) #from https://github.com/langcog/tidyboot
library(qdap)
library(tidyverse)

opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, 
               error = FALSE, cache = TRUE, tidy = FALSE)
```

This script loads in all of the raw, identifying data and writes it out to minimally-processed CSVs that can be shared publicly.

## Read Transcripts

Read in transcript data. We need to do this first to get the target items to pull out of the survey.
```{r read-transcripts}
transcripts <- list.files(here("raw_data/qcoded"), "*.csv", full.names = T)


read_transcript <- function(file) {
  
  transcript <- read_csv(file) %>%
    #mutate(id = parse_number(basename(file))) %>%
    mutate(id = str_split(file, "[//.]")[[1]] %>% tail(2) %>% head(1),
           id = gsub("q", "", id)) %>%
    #remove_empty("cols") %>%
    clean_names()
    
    # Pull out either parent or child's data
    pull_data <- function(person) {
      transcript %>%
        select(starts_with(person), descriptors:num_superordinate) %>%
        select_all(~gsub(paste0(person,"_"), "", .x)) %>%
        select_all(~gsub("utterance_", "", .x)) %>%
        mutate(person = person) %>%
        mutate(id = first(pull(transcript,id)))
    
    }
  
  # Tidy up
    pull_data("parent") %>%
      mutate(target = gsub("\\.", "", target) %>% tolower,
             utterance = gsub("\\?", " \\? ", utterance),
             utterance = gsub("\\.", " \\. ", utterance),
             utterance = gsub("\\!", " \\! ", utterance),
             utterance = gsub("\\,", " \\, ", utterance),
             utterance = str_squish(utterance)) 
}

tidy_data <- map_dfr(transcripts, read_transcript) %>%
  rename(row = ordinal)

targets <- tidy_data %>%
  filter(!is.na(target), target != "n/a") %>%
  distinct(target, .keep_all = T) %>%
  select(id, target) %>%  pull()

practice_targets <- c("artichoke", "apple") 
```

## Process vocabulary survey data

Reads in identifiable data from vocabulary surveys and combine with study identifiers 
```{r read-survey-data}
# Parent Survey Identifying Ids
qualtrics_data <- read_csv(here("raw_data/qualtrics_data.csv")) %>%
  slice(3:nrow(.)) %>%
  clean_names()

# Mapping between identifiable ids and non-identifiable ids
qualtrics_ids <- read_csv(here("raw_data/qualtrics_ids.csv")) %>%
  clean_names()

# Three batches of surveys were sent out
survey1 <- read_csv(here("raw_data/survey_link1.csv"))
survey2 <- read_csv(here("raw_data/survey_link2.csv"))
survey3 <- read_csv(here("raw_data/survey_link3.csv"))

vocab_data <- bind_rows(survey1, survey2, survey3) %>%
  clean_names() %>%
  filter(!is.na(response_id)) %>%
  left_join(qualtrics_data, by = "response_id") %>%
  select(link, q1) %>%
  left_join(qualtrics_ids, by = "link") %>%
  select(q1, response_id, number) %>%
  rename(video_id = response_id, study_id = number) %>%
  filter(!is.na(study_id))
```

Munge vocab data
```{r munge-vocab}
tidy_vocab <- vocab_data %>%
  unnest_tokens(word, q1) %>% 
  mutate(understands = T) %>%
  select(-video_id) %>%
  complete(study_id, word, fill = list(understands = F)) %>%
  left_join(select(vocab_data, -q1), by = "study_id")
```

Estimate the difficulty of each target word by computing the proportion of parents who report that their child knows it
```{r word_difficulty}
word_difficulty <- tidy_vocab %>%
  filter(word %in% targets, video_id %in% pull(tidy_data, id)) %>%
  group_by(word) %>%
  tidyboot_mean(understands) %>%
  rename(avg_known = empirical_stat) %>%
  arrange(desc(avg_known))
```

Compute total estimated vocabulary for each child (number of words their parent thought they knew), and write out children's vocabularies
```{r write_word_difficulty,}
total_vocab <- tidy_vocab %>%
  group_by(study_id) %>%
  summarise(vocab = sum(understands),
            possible_vocab = n())

subj_vocab <- tidy_vocab %>%
  select(study_id, word, understands) %>%
  filter(word %in% targets) %>%
  mutate(type = if_else(word %in% c("apple", "artichoke"), "practice",
         if_else(word %in% c("cat", "dog", "bird", "cow", "fish", "duck", 
                             "horse", "elephant"),
                 "early", "late")))%>%
  left_join(word_difficulty, by = "word") %>%
  left_join(total_vocab, by = "study_id") %>%
  select(-n)

subj_ids <- subj_vocab %>%
  select(study_id) %>%
  distinct() %>%
  mutate(subj = 1:n())

subj_vocab %>%
  left_join(subj_ids, by = "study_id") %>%
  select(subj, possible_vocab, vocab, type, word, avg_known, 
         understands, ci_lower, ci_upper) %>%
  write_csv(here("data/subj_vocab.csv"))
```

Read in data from the experiment (which animal was chosen on each trial)
```{r read-response}
child_response <- read_csv(here("raw_data/animalgame_data.csv")) %>%
  filter(!subj %in% c("xx", "Twst", "Test", "test"))

missing_data <- read_csv(here("raw_data/animalgame_missing.csv"))

filled_data <- bind_rows(child_response, missing_data) %>%
  rename(study_id = subj)

response_data <- left_join(vocab_data, filled_data, by = "study_id") %>%
  mutate(game_trial = trial_type != "practice") %>%
  arrange(study_id, game_trial, trial_num) %>%
  group_by(study_id) %>%
  mutate(trial_num = 1:n(),
         correct = correct == "Y")
```


Munge transcript data
```{r make_target_df}
# Identify trials by a change in target
trials <- tidy_data %>%
  group_by(id) %>%
  arrange(id, onset) %>%
  filter(target %in% targets) %>%
  mutate(new_trial = target != lag(target, default = TRUE),
         trial = cumsum(new_trial)) %>%
  select(id, row, target, trial)

# The target animal on each trial
trial_targets <- trials %>%
  distinct(id, trial, target) %>%
  rename(trial_target = target)

parent_data <- tidy_data %>%
  left_join(trials, by = c( "id", "row", "target")) %>%
  group_by(id) %>%
  fill(trial) %>%
  filter(!is.na(trial)) %>%
  group_by(id, trial) %>%
  mutate(selection = max(0, which(str_detect(selection, "selects")),
                             na.rm = T)) %>%
  mutate(phase = case_when(row_number() < selection ~ "pre",
                           row_number() == selection ~ "during",
                           T ~ "post") %>%
           factor(levels = c("pre", "during", "post"))) %>%
  left_join(trial_targets, c("id", "trial")) %>%
  group_by(id, trial_target) %>%
  mutate(appearance = factor(trial >= mean(trial))) %>%
  ungroup() %>%
  mutate(appearance = factor(appearance, labels = c("first", "second")),
         id = as.character(id))

target_data_gaps <- parent_data %>%
  mutate(length = wc(utterance),
         length = if_else(is.na(length), as.integer(0), length))

target_data <- target_data_gaps %>%
  left_join(select(vocab_data, video_id, study_id), 
            by = c("id" = "video_id")) %>%
  left_join(subj_ids, by = "study_id") %>%
  filter(phase != "during") %>%
  mutate(trial_type = if_else(trial_target %in% practice_targets, 
                              "practice", "game"),
         target = if_else(target == "n/a", as.character(NA),
                                target))

target_data %>%
  select(subj, row, trial_type, trial, phase, appearance, trial_target, target, 
         utterance, length, num_descriptors:num_superordinate) %>%
  pivot_longer(cols = num_descriptors:num_superordinate, 
               names_to = "descriptor", values_to = "descriptor_value") %>%
  mutate(descriptor_value = if_else(is.na(descriptor_value), 
                                    0, descriptor_value)) %>%
  pivot_wider(names_from = "descriptor", values_from = "descriptor_value") %>%
  select(-row) %>%
  arrange(subj, desc(trial_type), trial, phase) %>%
  write_csv(here("data/transcripts.csv"))

```

## Demographic data

Read in Demographic data with identifying information
```{r demographics}
demo_data <- read_csv(here("raw_data/animalgame_demo.csv"))
```

Write demographics out
```{r write_demos}
target_data %>%
  ungroup() %>%
  distinct(subj, study_id) %>%
  left_join(qualtrics_ids, by = c("study_id"="number")) %>%
  left_join(demo_data, by = c("response_id"="id")) %>%
  select(subj, age, gender, race, hispanic_latino, mom_ed) %>%
  rename(hispanic = hispanic_latino) %>%
  mutate(age_months = floor(age / 30.5),
         age_extra_days = floor(age - (age_months * 30.5)),
         age_years = age/365,
         gender = factor(gender, levels = c("f", "m"), 
                         labels = c("female", "male")),
         race = as.factor(race),
         mom_ed = as.factor(mom_ed),
         hispanic = factor(hispanic, levels = c("n", "y"), labels = c("no", "yes"))) %>%
  select(-age) %>%
  write_csv(here("data/demographics.csv"))

```

Test accuracy
```{r accuracy}
test_data <- response_data %>%
  left_join(subj_ids, by = c("study_id")) %>%
  ungroup() %>%
  select(subj, trial_num, trial_type, game_trial, target, correct, rt, pic1, 
         pic2, pic3, side_selected)

write_csv(test_data, here("data/test_data.csv"))
```
