---
title: "Parents Calibrate Speech to Children's Vocabulary Knowledge"
bibliography: animalgame.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
 \author{Ashley Leung, Alexandra Tunkel, and Daniel Yurovsky \\
         \texttt{\{ashleyleung, aetunkel, yurovsky\}@uchicago.edu} \\
        Department of Psychology \\ University of Chicago}

abstract:
    "Almost all children acquire language, yet the rates of development differ drastically across individuals. Previous research suggests that these differences may arise partially from disparities in parental input, a finding that has been the foundation for quantity-based intervention programs. However, language development is not simply absorbing input- language is social in nature. The communicative intent and interactive nature of language must not be ignored when considering how parental input influences children\\'s language development. Indeed, studies have shown that parental responsiveness shapes young children's language learning. Parental sensitivity (to children\\'s knowledge, intent, etc.) may thus be a better predictor of children\\'s language development than mere quantity of speech. The present study examined whether parents calibrate speech to their children\\'s knowledge in an interactive game. Our results show that parents modify their language according to beliefs about their children\\'s vocabulary knowledge, using longer sentences when describing unfamiliar objects, and shorter sentences for familiar objects."

keywords:
  "parent-child interaction; language development; communication"
    
output: cogsci2016::cogsci_paper
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)
```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(tidyverse)
library(forcats)
library(knitr)
library(tidytext)
library(readxl)
library(tidyboot)
library(stringr)
library(janitor)
library(here)
library(ggthemes)
library(lme4)
library(lmerTest)
library(directlabels)
library(ggrepel)

theme_set(theme_classic(base_size = 20))
```

# Introduction

Children learn language at astonishing rates, acquiring thousands of words by the time they are toddlers. How do children learn so many words even before they know how to dress themselves? One account for children's rapid language acquisition is statistical learning. Young children can attend to the distributional structure of language, learning to discriminate words and identify word order from speech streams [@Saffran1996; @Saffran2003]. Statistical learning can be a powerful tool for early language learning, and showcases the ability that children have to harvest information from their surroundings. However, children's language environments may also play a role in supporting language development.

The way we speak to children often differs from the way we speak to adults. Child-directed speech (CDS) exists across cultures, and is characterized by higher pitches and exaggerated enunciations [@Cooper1990; @Grieser1988]. Not only do children prefer CDS over adult-directed speech (ADS), CDS is also more helpful for language learning than overheard ADS [@Shneidman2013]. One reason why CDS may facilitate language development is that its structural qualities make speech segmentation and word learning easier [@Thiessen2005; @Yurovsky2016]. Parents also show sensitivity towards children's development, such that they use simpler and more redundant language when talking to toddlers, and more complex syntactic structures when speaking with school-age children [@Snow1972]. Children's language environments are uniquely suited for their abilities, and these environments change across development.

Why do parents modify the way they speak according to their children? One possible explanation is that parents are actively teaching their children. Indeed, some have posited that CDS is an ostensive cue for social learning, and that infants are born prepared to attend to these cues [@Csibra2009]. While it may be true that parents hope to impart knowledge to their children, we argue that effective communication is the proximal goal. The field of linguistics has long established that adults communicate in ways that are efficient. For example, Grice's (1975) maxim of quantity states that speech should be as informative as necessary, and no more. Adults are able to adhere to these maxims with relative ease, and it is likely that they do so regardless of who they are speaking to. That is, a parent's goal to communicate efficiently does not change depending on whether they are speaking to a child or an adult. Our account posits, therefore, that as parents seek to communicate with their children, they modify their language as a means to achieve successful communication.

# General Formatting Instructions 

For general information about authoring in markdown, see **[here](http://rmarkdown.rstudio.com/authoring_basics.html).**

For standard spoken papers and standard posters, the entire 
contribution (including figures, references, everything) can be 
no longer than six pages. For abstract posters, the entire contribution 
can be no longer than one page. For symposia, the entire contribution 
can be no longer than two pages.

The text of the paper should be formatted in two columns with an
overall width of 7 inches (17.8 cm) and length of 9.25 inches (23.5
cm), with 0.25 inches between the columns. Leave two line spaces
between the last author listed and the text of the paper. The left
margin should be 0.75 inches and the top margin should be 1 inch.
\textbf{The right and bottom margins will depend on whether you use
U.S. letter or A4 paper, so you must be sure to measure the width of
the printed text.} Use 10 point Times Roman with 12 point vertical
spacing, unless otherwise specified.

The title should be in 14 point, bold, and centered. The title should
be formatted with initial caps (the first letter of content words
capitalized and the rest lower case). Each author's name should appear
on a separate line, 11 point bold, and centered, with the author's
email address in parentheses. Under each author's name list the
author's affiliation and postal address in ordinary 10 point  type.

Indent the first line of each paragraph by 1/8~inch (except for the
first paragraph of a new section). Do not add extra vertical space
between paragraphs.

# First-Level Headings

First level headings should be in 12 point , initial caps, bold and
centered. Leave one line space above the heading and 1/4~line space
below the heading.

## Second-Level Headings

Second level headings should be 11 point , initial caps, bold, and
flush left. Leave one line space above the heading and 1/4~ line
space below the heading.

### Third-Level Headings

Third-level headings should be 10 point , initial caps, bold, and flush
left. Leave one line space above the heading, but no space after the
heading.

# Formalities, Footnotes, and Floats

Use standard APA citation format. Citations within the text should
include the author's last name and year. If the authors' names are
included in the sentence, place only the year in parentheses, as in
[-@NewellSimon1972a], but otherwise place the entire reference in
parentheses with the authors and year separated by a comma
[@NewellSimon1972a]. List multiple references alphabetically and
separate them by semicolons [@ChalnickBillman1988a; @NewellSimon1972a]. 
Use the et. al. construction only after listing all the authors to a
publication in an earlier reference and for citations with four or
more authors.

For more information on citations in RMarkdown, see **[here](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html#citations).**

## Footnotes

Indicate footnotes with a number\footnote{Sample of the first
footnote.} in the text. Place the footnotes in 9 point type at the
bottom of the page on which they appear. Precede the footnote with a
horizontal rule.\footnote{Sample of the second footnote.} You can also use 
markdown formatting to include footnotes using this syntax [^1].

[^1]: Sample of a markdown footnote.

## Figures

All artwork must be very dark for purposes of reproduction and should
not be hand drawn. Number figures sequentially, placing the figure
number and caption, in 10 point, after the figure with one line space
above the caption and one line space below it. If necessary, leave extra white space at
the bottom of the page to avoid splitting the figure and figure
caption. You may float figures to the top or bottom of a column, or
set wide figures across both columns.

## Two-column images

You can read local images using png package for example and plot 
it like a regular plot using grid.raster from the grid package. 
With this method you have full control of the size of your image. **Note: Image must be in .png file format for the readPNG function to work.**

You might want to display a wide figure across both columns. To do this, you change the `fig.env` chunk option to `figure*`. To align the image in the center of the page, set `fig.align` option to `center`. To format the width of your caption text, you set the `num.cols.cap` option to `2`.

```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns. And the caption text is limited to 0.8 of the width of the document."}
img <- png::readPNG("figs/walrus.png")
grid::grid.raster(img)
```

## One-column images

Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.

```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
img <- png::readPNG("figs/lab_logo_stanford.png")
grid::grid.raster(img)
```


## R Plots

You can use R chunks directly to plot graphs. And you can use latex floats in the
fig.pos chunk option to have more control over the location of your plot on the page. For more information on latex placement specifiers see **[here](https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions)**

```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
x <- 0:100
y <- 2 * (x + rnorm(length(x), sd = 3) + 3)

ggplot2::ggplot(data = data.frame(x, y), 
       aes(x = x, y = y)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```


## Tables

Number tables consecutively; place the table number and title (in
10 point) above the table with one line space above the caption and
one line space below it, as in Table 1. You may float
tables to the top or bottom of a column, set wide tables across both
columns.

You can use the xtable function in the xtable package.

```{r xtable, results="asis"}
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
out <- lm(y ~ x)

tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
                      caption = "This table prints across one column.")

print(tab1, type="latex", comment = F, table.placement = "H")
```

# Acknowledgements

Place acknowledgments (including funding information) in a section at
the end of the paper.

# References 

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
